Effects of Different Pain Relievers and Dosages on Cognitive Retention

### 2025-04-10 paper/paper.qmd
Changes in Conclusion

We performed a Two- way ANOVA to evaluate whether different types of pain relievers (Aspirin, Paracetamol, Tramadol, and Placebo) influence cognitive performance measured through memory game performance to address our research question 1. The null hypothesis proposed that all pain relievers produce equal effects on memory performance, while the alternative hypothesis suggests that at least one type differs significantly. The ANOVA results indicated that there was no statistical significant difference in memory game score between the four pain relievers under main effects. These results indicate that, at the standard dosages, none of the pain relievers significantly affected cognitive performance. This supports the interpretation that commonly used pain relievers neither impair nor enhance cognitive performance in the context of memory games performance. To answer research question 2, we employed the same Two-way ANOVA model to assess whether an interaction exists between the type of pain reliever (Aspirin, Paracetamol, Tramadol, and Placebo) and dosage level (low/high) on memory game performance. The analysis revealed no statistically significant interaction effect (p=0.24), leading us to fail to reject the null hypothesis. This indicates that the effect of pain reliever type on cognitive performance does not vary meaningfully across dosage levels, and vice versa. Specifically, the ANOVA results demonstrated that the interaction term between drug type and dosage level did not reach significance, suggesting that dosage adjustments do not modify the cognitive effects of the tested pain relievers. This study did not find clear evidence that pain relievers or their dosages have a significant impact on cognitive retention. However, the exploratory trends observed, particularly with Paracetamol and Tramadol, highlight the need for larger-scale studies to investigate subtle or context-dependent effects. Future research could incorporate longitudinal designs, broader age-specific analyses, and alternative cognitive metrics to deepen understanding of painkillers’ cognitive implications. This study did not find clear evidence that pain relievers or their dosages have a significant impact on cognitive retention. However, the exploratory trends observed, particularly with Paracetamol and Tramadol, highlight the need for larger-scale studies to investigate subtle or context-dependent effects. Future research could incorporate longitudinal designs, broader age-specific analyses, and alternative cognitive metrics to deepen understanding of painkillers’ cognitive implications.

>>>>

We performed a Two-way ANOVA to evaluate whether different types of pain relievers (Aspirin, Paracetamol, Tramadol, and Placebo) influence cognitive performance measured through memory game performance to address our research question 1. The null hypothesis proposed that all pain relievers produce equal effects on memory performance, while the alternative hypothesis suggests that at least one type differs significantly. The ANOVA results indicated that there was no statistical significant difference in memory game score between the four pain relievers under main effects. These results indicate that, at the standard dosages, none of the pain relievers significantly affected cognitive performance. This supports the interpretation that commonly used pain relievers neither impair nor enhance cognitive performance in the context of memory games performance. To answer research question 2, we employed the same Two-way ANOVA model to assess whether an interaction exists between the type of pain reliever (Aspirin, Paracetamol, Tramadol, and Placebo) and dosage level (low/high) on memory game performance. The analysis revealed no statistically significant interaction effect (p=0.24), leading us to fail to reject the null hypothesis. This indicates that the effect of pain reliever type on cognitive performance does not vary meaningfully across dosage levels, and vice versa. Specifically, the ANOVA results demonstrated that the interaction term between drug type and dosage level did not reach significance, suggesting that dosage adjustments do not modify the cognitive effects of the tested pain relievers.

This study did not find clear evidence that pain relievers or their dosages have a significant impact on cognitive retention. However, the exploratory trends observed, particularly with Paracetamol and Tramadol, highlight the need for larger-scale studies to investigate subtle or context-dependent effects. Future research could incorporate longitudinal designs, broader age-specific analyses, and alternative cognitive metrics to deepen understanding of painkillers’ cognitive implications. This study did not find clear evidence that pain relievers or their dosages have a significant impact on cognitive retention.
